### 2009-01-19 articles/2009/geoinformatics/article.tex
small change
git-svn-id: https://svn.osgeo.org/qgis/trunk@9964 c8812cc2-4d05-0410-92ff-de0c093fc19c
small updates
git-svn-id: https://svn.osgeo.org/qgis/trunk@9981 c8812cc2-4d05-0410-92ff-de0c093fc19c

\subsection{QGIS is Open Source}

The QGIS project is carried out largely by a group of developers,
translators, documenters, release helpers, bug reporters and promoters. All
these volunteers together with a large number of users make up the QGIS
comunity, which in time has built up a comprehensive, valuable and useful
code and documentation base free to use and improve for everybody.

@@

@@

\subsection{Conclusion}

>>>>

\subsection{QGIS Open Source Community}

The QGIS project is Open Source and carried out largely by a group of
developers, translators, documenters, release helpers, bug reporters, and
promoters. All these volunteers together with a large number of users make up
the QGIS comunity, which in time has built up a comprehensive, valuable and
useful code and documentation base free to use and improve for everybody.

@@

There are several possibilities to get in contact with the QGIS project. 
A prefered way is is by joining the qgis-users mailing list or the QGIS Forum.

@@

\subsection{Perspective / Conclusion}
